*Prochlorococcus marinus* responses to light and oxygen

### 2024-03-11 Code/Manuscript_O2.Rmd
minor edits

We used the OceansMap Protein Portal (OPP;
<https://proteinportal.whoi.edu/>) [@saitoDevelopmentOceanProtein2021]
to analyze the distribution of proteins from clades of *P. marinus* in
samples taken across a range of [O~2~] and depth, which in turn
correlates to peak light at the site of sampling. In parallel we
analyzed the growth and physiological responses of representative
strains from three clades of *P. marinus* under a matrix of [O~2~],
light levels, spectral waveband ranges, and photoperiods, to approximate
eco-physiological conditions representative of current and hypothetical
future ocean zones. *Prochlorococcus marinus* MED4, a clade HLI strain,
was isolated near the ocean surface (5m depth) of the Mediterranean Sea
where [O~2~] is near saturation, light levels are high and spectral bias
from full solar irradiance is minimal. *Prochlorococcus marinus* SS120,
a clade LLII/III strain, was isolated from the Sargasso Sea at a depth
of 120 m, while *P. marinus* MIT9313, a clade LLIV strain, was isolated
from the North Atlantic Gulf Stream at a depth of 135 m
[@moorePhotophysiologyMarineCyanobacterium1999]. At these depths, light
attenuation and spectral shifts occur, resulting in low blue light,
while [O~2~] varies from near-surface saturation levels to decreased
concentrations, but does not necessarily decrease systematically with
depth [@billheimerOxygenSeasonalityUtilization2021].

@@

knitr::kable(FtsHTable,
             caption = "FtsH protease homologs in *Prochlorococcus marinus* and the model cyanobacterium *Synechocystis* sp. PCC6803. Protein homology determined by multiple sequence alignment with MUSCLE followed by construction of maximum likelihood phylogenetic tree using 1000 bootstrap replicates in MEGAX.",
              col.names =  c("Organism",
                          "Homolog 1",
                          "Homolog 2",
                          "Homolog 3",
                          "Homolog 4"),
               align = "lcccc"
             )
```

>>>>

We used the OceansMap Protein Portal (OPP;
<https://proteinportal.whoi.edu/>) [@saitoDevelopmentOceanProtein2021]
to analyze the distribution of proteins from clades of *P. marinus* in
samples taken across a range of [O~2~] and depth, which in turn
correlates to depth attenuated peak light at the site of sampling. In parallel we
analyzed the growth and physiological responses of representative
strains from three clades of *P. marinus* under a matrix of [O~2~],
light levels, spectral waveband ranges, and photoperiods, to approximate
eco-physiological conditions representative of current and hypothetical
future ocean zones. *Prochlorococcus marinus* MED4, a clade HLI strain,
was isolated near the ocean surface (5m depth) of the Mediterranean Sea
where [O~2~] is near saturation, light levels are high and spectral bias
from full solar irradiance is minimal. *Prochlorococcus marinus* SS120,
a clade LLII/III strain, was isolated from the Sargasso Sea at a depth
of 120 m, while *P. marinus* MIT9313, a clade LLIV strain, was isolated
from the North Atlantic Gulf Stream at a depth of 135 m
[@moorePhotophysiologyMarineCyanobacterium1999]. At these depths, light
attenuation and spectral shifts occur, resulting in low blue light,
while [O~2~] varies from near-surface saturation levels to decreased
concentrations, but does not necessarily decrease systematically with
depth [@billheimerOxygenSeasonalityUtilization2021].

@@

knitr::kable(FtsHTable,
             caption = "FtsH protease homologs in *Prochlorococcus marinus* and the model cyanobacterium *Synechocystis* sp. PCC6803. Protein homologies between *Prochlorococcus* and *Synechocystis* were determined by multiple sequence alignment with MUSCLE followed by construction of maximum likelihood phylogenetic tree using 1000 bootstrap replicates in MEGAX.",
              col.names =  c("Organism",
                          "Homolog 1",
                          "Homolog 2",
                          "Homolog 3",
                          "Homolog 4"),
               align = "lcccc"
             )
```
